Data Visualization

### 2023-01-27 src/data_viz.Rmd
started bar chart

library(googlesheets4)
library(tidyverse)
library(janitor)

@@

```{r}
total_scores_data <- read_sheet("https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=1307699202")

@@

>>>>

library(googlesheets4)
library(tidyverse)
library(janitor)
library(ggplot2)

@@

```{r}
total_score_data <- read_sheet("https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=1307699202") %>% 
  rename(financial_score = normalized_irr,
         climate_impact = inverted_n_total_co2,
         health_impact = inverted_n_health_emissions_cost,
         energy_production = normalized_annual_renewable,
         climate_risk = normalized_inverted_climate_risk)

@@

```{r}
score_tidy <- total_score_data %>%

```{r}

ggplot(data = total_score_data, aes(y = city_msa, x = total_score_owen)) + 
    geom_bar(position="stack", stat="identity")
```
